---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "**`[[`**Your Name**`]]`**"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```

If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
```{r 1}
ggplot(covid_data_count,aes(x = Cases, y = Deaths, color = race)) + geom_point()
```
The plot shows the relationship between the number of Covid cases and deaths and colored by races. According to the plot, most points clustered at where the number of cases is in the interval [0e+00, 1e+06] and the number of deaths is in the interval [0, 20000]. At the same time, there is a clear positive relationship between Covid Cases and Deaths. 

2. Are there any conclusions you can draw?
A possible conclusion can be drawn from the plot above is that as the number of Covid cases rises, the number of deaths will also increase. 

3. What were you not able to do due to not having the R knowledge?
The thing that I'm not able to do due to not having the R knowledge is finding the equation that can best describe the relationship between the number of Covid cases and deaths, which can be used to make predictions. 

4. What other data would be useful to better understand this data?
The data that would be useful to better understand this data include the number of people who are vaccinated everyday, the number of people who are quarantined everyday, and the number of people who have recovered from Covid everyday. 
